Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
xD

​\Section{Introduction}
Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs. The abstraction level has been increased with help of compilers, object-oriented programming (OOP) and Unified Modelling Language (UML). The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate OOP code \cite{staron2006adopting}.

@@

\SubSection{Statement of the Problem}
Companies don't know if adopting MDD will be beneficial in terms of money and improved software quality.

>>>>

​\Section{Introduction}
Ever since the first computer programs were written, researchers and developers have been working on new programming concepts in order to decrease the level of complexity needed to develop programs. The abstraction level has been increased with help of compilers, object-oriented programming and Unified Modelling Language (UML). The current trend within software engineering (SE) is Model-driven Software Development (MDSD) which uses UML to generate object-oriented code \cite{staron2006adopting}.

@@

\SubSection{Statement of the Problem}
The selection of development process, programming language and programming paradigm has a high impact on the development speed depending on what the the system requirements are and in which environment the system is developed. Selecting for example MDSD for the wrong system and setting may have a very negative impact on development speed, quality and maintainability. Since there seems to be a consensus in academia that MDSD is the future, and that most large software companies chose not to adopt MDSD, there is a need to methodically investigate the existing literature in which studies of the adoption of MDSD, and advantages and disadvantages of MDSD.
